---
title: "615Midtermmmmmmm"
author: "Kaiyu Yan,Si Chen, Wenjia Xie, Siwei Hu"
date: "October 17, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


We sned email to noaa.com and asked for their weather data. They send us a Data with 18 variables which are different types of weather and max/min temperature. We choose 7 different types of weatherand changes their jorgon to normal words like"snowy" "fog" to help us understand what happen.We make a new column called "type" and then we build a double for loop in order to get weather type everyday. 
```{r}
##### new
##### Weather Data #####

weather_data <- read.csv("weather data.csv")
colnames(weather_data)[colnames(weather_data)=="DATE"] <- "Date"

weather_data$Date <- as.Date(weather_data$Date,"%Y-%m-%d")
typelist = c("Fog","Mist","Drizze","Rain","Snow","Thunder","Heavy fog")
type_code = c("WT01","WT13","WT14","WT16","WT18","WT03","WT02")
weather_data$type<-NA

for (i in 1:length(typelist)) {
  colnames(weather_data)[which(colnames(weather_data)==type_code[i])] = typelist[i]
}

weather_data[is.null(weather_data)] <- NA
##Run through all types to get the weather of a certain day, add that to the "type" column
for (m in 1:dim(weather_data)[1]) {
  t<-0
  for (n in 1:length(typelist)) {
    if (is.null(weather_data[m,typelist[n]])) {
      weather_data[m,typelist[n]] = NA
    }
    if (!is.na(weather_data[m,typelist[n]])) {
      weather_data[m,"type"] =  typelist[n]
      t<-t+1
    }
  }
  if(t==0)
    weather_data[m,"type"] = "normal"
}
```

```{r}
year<-c(2012:2017)
for (i in 1:6){
weather_year<-filter(weather_data,str_detect(Date,as.character(year[i])))
pic<-ggplot(data = weather_year) +
  aes(x = type, y = TAVG, color = type) +
  geom_boxplot(fill = "#0c4c8a",notch = FALSE) 
  theme_minimal()
print(pic)
}
```


We got Basketball data from "baskerball-reference". We write code to grab data from their website from 2012 to 2017 season. In this chuck i put code that how we grab data from website and how we build the dataframe. Since we finish the data frame, we export it to be a .csv file for convenience.
```{r}
# library(xml2)
# library(rvest)
# library(tidyverse)
# site1 <- "https://www.basketball-reference.com/leagues/NBA_"
# site2 <- "_games-"
# site3 <- ".html"
# year <- c(2013:2018)
# month <- c("january","february","march","april","may","june","october","november","december")
# month_index<-c(1:9)
# year_index<-c(1:6)
# name1<-c()
# name2<-c()
# total.date<-c()
# total.attdence<-c()
# for (i in year_index){
#   for (j in month_index){
#     site<-paste(site1,year[i],site2,month[j],site3,sep="")
#     webpage<-read_html(site)
#     name1<- webpage %>% html_nodes('.left:nth-child(1)') %>% html_attrs()
#     name2<- webpage %>% html_nodes('.center+.right') %>% html_text()
#     total.date <- c(total.date,name1)
#     total.attdence <- c(total.attdence,name2)
#     j<-j+1
#   }
#   i<-i+1
# }
# total.date1 <- t(data.frame((total.date)))[,4]
# total.attdence1 <- data.frame(total.attdence)
# b_data<-cbind(total.date1,total.attdence1)[-1,]
# colnames(b_data)<-c("date","attendance")
# rownames(b_data)<-rep(1:7934)
# host<-substr(b_data$date, 10, 12)
# b_data$date<-substr(b_data$date,1,8)
# b_data3<-cbind(b_data,host)
# write.csv(b_data3,'basketball.csv') 

```


Then we grab host variable with string "BOS" to get date when Celitics play in their host "TD Garden". Because date we grab have one more 0 like"201201010". So we use substring to cut out only 8 digitals and convert date type to "yyyy-mm-dd" in order to join with weather data. 
```{r}

##### Basketball Data Only #####



Basketball<-read.csv("basketball.csv")
Homegame <- filter(Basketball,str_detect(host,"BOS"))
Homegame$date <- substring(Homegame$date, 1,8)
Homegame$date <- as.Date(Homegame$date,"%Y%m%d")
names(Homegame)[2]<-paste("Date")
names(Homegame)[3]<-paste("Attendance")
```

We got Baseball data from "baseball-reference". We write code to grab data from their website from 2012 to 2017 season. In this chuck i put code that how we grab data from website and how we build the dataframe. Since we finish the data frame, we export it to be a .csv file for convenience.
Btw, we grab baseball data each year because the baseball season is from April to October. 

```{r}
# site1 <-"https://www.baseball-reference.com/teams/BOS/"
#site2 <- "-schedule-scores.shtml"
# year <- c(2013:2018)
# month_index<-c(1:9)
# year_index<-c(1:6)
# name1<-c()
# name2<-c()
# total.date<-c()
# total.attdence<-c()
# for (i in year_index){
#   for (j in month_index){
#     site<-paste(site1,year[i],site2,sep="")
#     webpage<-read_html(site)
#     name1<- webpage %>% html_nodes('.left:nth-child(1)') %>% html_attrs()
#     name2<- webpage %>% html_nodes('.center+.right') %>% html_text()
#     total.date <- c(total.date,name1)
#     total.attdence <- c(total.attdence,name2)
#     j<-j+1
#   }
#   i<-i+1
# }
# 
# total.date1 <- t(data.frame((total.date)))[,4]
# total.attdence1 <- data.frame(total.attdence)
# b_data<-cbind(total.date1,total.attdence1)[-1,]
# colnames(b_data)<-c("date","attendance")
# rownames(b_data)<-rep(1:7934)
# host<-substr(b_data$date, 10, 12)
# b_data$date<-substr(b_data$date,1,9)
# b_data3<-cbind(b_data,host)
# 
# class(b_data3$attendance)
# write.csv(b_data3,'Baseball.csv')
```

WE select several variable include Date, Attendance, year and etc. Since the date of base is like "Sunday,04,11", we seperate "Sunday","04","11" to three different columns and merge year,month and day to be a new date variable, use filter function to get host information. We spend a lot of time to change this date type to become same as the date type in weather data. Final we get date type like "yyyy-mm-dd".
```{r}
####### Baseball Data Only #######
Baseball <- read.csv("Baseball.csv")
Clean_1 <- select(Baseball, Date, Tm:Opp, Attendance,Year)
Clean_2 <- data.frame(do.call('rbind', strsplit(as.character(Clean_1$Date),',',fixed=TRUE)))
Clean_2 <- data.frame(do.call('rbind', strsplit(as.character(Clean_2$X2),' ',fixed=TRUE)))
Clean_1 <- merge(Clean_1,Clean_2,by = 0)
Clean_3<- filter(Clean_1, !str_detect(Var.5,"@"))
Clean_4 <- filter(Clean_3,str_detect(Tm,"BOS"))
Clean_5 <- select(Clean_4, 6,7,9,10)
Clean_5$X2 <- match(Clean_5$X2,month.abb)
Baseball_All<- unite(Clean_5,Date,2:4,sep = "-",remove = TRUE) 
Baseball_All$Date <- as.Date(Baseball_All$Date,"%Y-%m-%d")
```

We use inner_join to get weather data only when these two teams played in their host. 

```{r}
##### Basketball Join Weather ######
Celtics_All <- inner_join(Homegame,weather_data,by = "Date", match = all) 
Celtics_All <- select(Celtics_All,Date,Attendance,TAVG,type)
Celtics_All$Attendance <-  as.numeric(as.character(Celtics_All$Attendance))

#Full baseball data for each year
for(i in 2012:2017) { 
  assign(paste("Celtics",i,sep="_"),filter(Celtics_All,str_detect(Date,paste(i))))

} 
```
```{r}
##### Baseball Join Weather #####
Redsox_All <- inner_join(Baseball_All,weather_data,by = "Date", match = all) 
Redsox_All <- select(Redsox_All,Date,Attendance,TAVG,type)
Redsox_All$Attendance <-  as.numeric(as.character(Redsox_All$Attendance))

#Full baseball data for each year
for(i in 2012:2017) { 
  assign(paste("Redsox",i,sep="_"),filter(Redsox_All,str_detect(Date,paste(i))))

} 
```

```{r}
ggplot(data = Redsox_All,aes(x = Date, y = Attendance, color = TAVG))+geom_point( ) 

ggplot(data = Redsox_All) +
  geom_smooth(mapping = aes( x = TAVG, y = Attendance, color = type), se = F)

Dataset= list(Redsox_2012,Redsox_2013,Redsox_2014,Redsox_2015,Redsox_2016,Redsox_2017)

for(i in 1:6){ 
  p<- ggplot(data = Dataset[[i]],aes(x = TAVG, y = Attendance,  color = type))+
    geom_point()+geom_smooth(se=F)
    print(p)
    }


 

```




```{r}
Dataset2= list(Celtics_2012,Celtics_2013,Celtics_2014,Celtics_2015,Celtics_2016,Celtics_2017)


for(i in 1:6){ 
  q <- ggplot(data = Dataset2[[i]],aes(x = TAVG, y = Attendance,  color = type))+
    geom_point()+geom_smooth(se=F)
    print(q)
  
 
    }

```